---
title: "Ware Dec_Prop_Site 6"
author: "Beth Sawyer"
date: "October 5, 2018"
output:
  html_document: default
  pdf_document: default
---
BCS, 10.1.18 updated for ASV2018 Site 6 houses paper
Updated with quadrat clusters updated from previous groupings; updated in Dec 2018, after ASV

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(RPostgreSQL)
require(ggplot2)
require(reshape2)
require(dplyr)
require(plotly)
require(gridExtra)
```

## Query DAACS using SQL code wrapper

```{r SQL query}

# tell DBI which driver to use
pgSQL <- dbDriver("PostgreSQL")
# establish the connection
DRCcon<-dbConnect(pgSQL, host='drc.iath.virginia.edu', port='5432',
                  dbname='daacs-production',
                  user='drcquery', password='!queryacct!')

Site6Full<-dbGetQuery(DRCcon,'
              SELECT
                   "public"."tblContext"."QuadratID",
                   "public"."tblContext"."ProjectID",
                   "public"."tblCeramic"."Quantity",
                   "public"."tblCeramicWare"."Ware",
                   "public"."tblCeramicGenre"."CeramicGenre"
                   FROM
                   "public"."tblContext"
                   INNER JOIN "public"."tblContextSample" ON "public"."tblContextSample"."ContextAutoID" = "public"."tblContext"."ContextAutoID"
                   INNER JOIN "public"."tblGenerateContextArtifactID" ON "public"."tblContextSample"."ContextSampleID" = "public"."tblGenerateContextArtifactID"."ContextSampleID"
                   INNER JOIN "public"."tblCeramic" ON "public"."tblCeramic"."GenerateContextArtifactID" = "public"."tblGenerateContextArtifactID"."GenerateContextArtifactID"
                   INNER JOIN "public"."tblCeramicWare" ON "public"."tblCeramic"."WareID" = "public"."tblCeramicWare"."WareID"
                   INNER JOIN "public"."tblCeramicGenre" ON "public"."tblCeramic"."CeramicGenreID" = "public"."tblCeramicGenre"."CeramicGenreID"
                   WHERE
                   
                   ((
                   "public"."tblContext"."ProjectID" =  \'106\') AND
                   (("public"."tblCeramicWare"."Ware" = \'Creamware\') OR ("public"."tblCeramicWare"."Ware" = \'Pearlware\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Porcelain, Chinese\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Delftware, Dutch/British\') OR ("public"."tblCeramicWare"."Ware" = \'Jackfield Type\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Nottingham\') OR ("public"."tblCeramicWare"."Ware" = \'Staffordshire Brown Stoneware\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Whieldon-type Ware\') OR ("public"."tblCeramicWare"."Ware" = \'White Salt Glaze\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Rosso Antico\') OR ("public"."tblCeramicWare"."Ware" = \'Turner Type\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Coarse earthenware, unidentified\') OR ("public"."tblCeramicWare"."Ware" = \'Porcelain, unidentifiable\')
                   OR ("public"."tblCeramicWare"."Ware" = \'British Stoneware\') OR ("public"."tblCeramicWare"."Ware" = \'Buckley-Type\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Astbury\') OR ("public"."tblCeramicWare"."Ware" = \'Black Basalt\') OR ("public"."tblCeramicWare"."Ware" = \'American Stoneware\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Redware\') OR ("public"."tblCeramicWare"."Ware" = \'Canary Ware\') OR ("public"."tblCeramicWare"."Ware" = \'Jasperware Type\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Iberian Ware\') OR ("public"."tblCeramicWare"."Ware" = \'Fulham Type\') OR ("public"."tblCeramicWare"."Ware" = \'Westerwald\')
                   OR ("public"."tblCeramicWare"."Ware" = \'Slipware, North Midlands/Staffordshire\')
                   ))
                   '
                   )
                   

```

##Data manipulation
Take out non-Genre sherds and put into a new dataframe. In full dataframe, make a new column that denotes decoration y/n to be used later.
```{r Take out non-Genre sherds}
Site6 <- subset(Site6Full, ! Site6Full$CeramicGenre  %in%  
                       c('Not Applicable'))

Site6_Full <- Site6Full %>%
  mutate(decoration = ifelse(CeramicGenre == 'Not Applicable', 'no', 'yes'))
```

Assign quadrats to site areas. Only North and South will be used for this analysis, but all quadrats were given an area designation.
```{r Assign quadrats to site areas}
Site6_Full <- Site6_Full
  Site6_Full$Area[(grepl("^013", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^014", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^016", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^028", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^029", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^030", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^031", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^032", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^033", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^034", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^035", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^036", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^037", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^040", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^043", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^044", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^045", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^046", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^047", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^048", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^051", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^052", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^053", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^054", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^055", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^056", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^057", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^058", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^059", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^061", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^062", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^065", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^066", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^069", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^070", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^071", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^072", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^073", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^074", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^075", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^078", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^079", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^080", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^081", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^083", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^084", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^085", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^086", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^087", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^097", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^098", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^099", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^100", Site6_Full$QuadratID))] <- 'North'
Site6_Full$Area[(grepl("^106", Site6_Full$QuadratID))] <- 'North'


  Site6_Full$Area[(grepl("^002", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^012", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^015", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^019", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^020", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^021", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^023", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^024", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^025", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^041", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^042", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^049", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^050", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^060", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^063", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^064", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^067", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^068", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^076", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^077", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^089", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^090", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^092", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^093", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^094", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^095", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^096", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^101", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^102", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^103", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^104", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^110", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^111", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^112", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^113", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^117", Site6_Full$QuadratID))] <- 'South'
  Site6_Full$Area[(grepl("^118", Site6_Full$QuadratID))] <- 'South'

  Site6_Full$Area[(grepl("^001", Site6_Full$QuadratID))] <- 'Souteast'
  Site6_Full$Area[(grepl("^004", Site6_Full$QuadratID))] <- 'Souteast'
  Site6_Full$Area[(grepl("^027", Site6_Full$QuadratID))] <- 'Souteast'
  Site6_Full$Area[(grepl("^108", Site6_Full$QuadratID))] <- 'Souteast'
  Site6_Full$Area[(grepl("^109", Site6_Full$QuadratID))] <- 'Souteast'
  Site6_Full$Area[(grepl("^114", Site6_Full$QuadratID))] <- 'Souteast'
  Site6_Full$Area[(grepl("^115", Site6_Full$QuadratID))] <- 'Souteast'

  Site6_Full$Area[(grepl("^003", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^005", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^006", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^007", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^008", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^009", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^010", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^011", Site6_Full$QuadratID))] <- 'SW Stone'
  Site6_Full$Area[(grepl("^022", Site6_Full$QuadratID))] <- 'SW Stone'

  Site6_Full$Area[(grepl("^038", Site6_Full$QuadratID))] <- 'Buffer'  
  Site6_Full$Area[(grepl("^039", Site6_Full$QuadratID))] <- 'Buffer'  
  Site6_Full$Area[(grepl("^026", Site6_Full$QuadratID))] <- 'Buffer'  
  Site6_Full$Area[(grepl("^017", Site6_Full$QuadratID))] <- 'Buffer'  
  Site6_Full$Area[(grepl("^018", Site6_Full$QuadratID))] <- 'Buffer'  
  Site6_Full$Area[(grepl("^091", Site6_Full$QuadratID))] <- 'Buffer'  
  Site6_Full$Area[(grepl("^107", Site6_Full$QuadratID))] <- 'Buffer'
```


Keep only North and South; make new column for ware type and genre combined. Also reassign generes to groups
```{r tidy up and add column}
  Site6_Areas1 <- Site6_Full %>%
    filter(Area %in% c('North', 'South'))%>%
    filter(decoration != 'no')%>%
    filter(Ware != 'American Stoneware')
  

Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'An Hua'] <- 'An Hua'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Barley'] <- 'Molded Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Blue and Gray'] <- 'Blue and Gray'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Feather Edge'] <- 'Molded Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Handpainted Blue'] <- 'Handpainted'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Molded Edge Decoration, other'] <- 'Molded Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Overglaze, handpainted'] <- 'Handpainted'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Handpainted, Polychrome Cool'] <- 'Handpainted'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Handpainted, Polychrome Other'] <- 'Handpainted'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Handpainted, Polychrome Warm'] <- 'Polychrome'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Royal Pattern'] <- 'Molded Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Scratch Blue'] <- 'Scratch Blue'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Shell Edge, blue'] <- 'Shell Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Shell Edge, green'] <- 'Shell Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Shell Edge, unid.'] <- 'Shell Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Slipware, factory made'] <- 'Slipware'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Sponge/Spatter'] <- 'Sponge/Spatter'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Over'] <- 'Printed over'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Under, black'] <- 'Printed under'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Under, blue'] <- 'Printed under'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Under, brown'] <- 'Printed under' 
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Under, green'] <- 'Printed under' 
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Under, light blue'] <- 'Printed under'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Transfer Print Under, unidentifiable'] <- 'Printed under'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Queen\'s Edge'] <- 'Molded Edge'
Site6_Areas1$GenreStyle[Site6_Areas1$CeramicGenre == 'Flow, transfer print blue'] <- 'Printed under'


```

Aggregate by WareGenre and areas and generate sums per area using summarise function. Note these computations are only for decorated sherds. 
```{r aggregate by areas}
WareGenSite6  <- Site6_Areas1 %>%
  group_by(Area, WareGen)%>%
  summarise(total = n())
```

Calculate relative frequencies.
```{r rel_freq}
Site6_Areas2 <- WareGenSite6%>%
  mutate(allceramics = sum(total))%>%
  mutate(rel_freq = (total/allceramics))
```

Do calculations for undecorated versus decorated proportions. First, aggregate by areas
```{r area aggregation}
Dec_Check <- Site6_Full%>%
  group_by(Area, decoration)%>%
  filter(Area %in% c('North', 'South'))%>%
  summarise(total = n())
```

Calculate relative frequencies for undecorated sherds by area.
```{r rel_freq}
Dec_Check2 <- Dec_Check%>%
  mutate(Area_Sum = sum(total))%>%
  mutate(Proportion = (total/Area_Sum))

e<-head(Dec_Check2 [, 1:5], theme = e)
e
write.csv(e, file='Decoration.csv')
```

##Graphs and outputs

```{r side-by-side bar graph}
Site6_Areas2%>%
  filter(WareGen != '%NA')

a<- ggplot(data=Site6_Areas2, aes(x=WareGen, y=rel_freq, fill=Area)) +
  geom_bar(stat="identity", position=position_dodge())+
  theme(axis.text.x=element_text(angle = 45, hjust = 1))+
  labs(title = "Proportion of Genre Type amongst Decorated Sherds", x="Ware Type and Genre", y="Proportion", cex.lab = 14)+
  scale_fill_brewer(palette = "Dark2")
a

ggsave("Decorated Props.jpg", a, width=11, height=7.5, dpi=600)

  
```

























